### 2021-02-22 yfcc100m/paper/vldb2021/design.tex
Update intro and design, minor changes in eval

In this section, we describe VDMS design principles and implementation,
which was briefly introduced in previous work \cite{vdms-nips}.
Figure \ref{fig:arch} depicts the high-level architecture of VDMS.
VDMS implements a client-server architecture that handles client
requests concurrently, and coordinates query execution across
the metadata and visual data components in order to return a unified response.
Users interact with both metadata and visual data
(i.e., images, videos, feature vectors) using a unified API,
in a transactional manner.

@@

The client library implements TCP/IP based connectors to the VDMS Server,
similar to most database\cite{memsql, mysql}.
Users can connect to VDMS and implement queries using VDMS' API
by defining JSON commands conforming to the query protocol we have defined.
The client library provides a simple method that
accepts a JSON string and an array or vector of blobs.
Internally, the library wraps the query string and blob using
Google Protobufs \cite{protobufs} and sends it to the VDMS server.
It also receives a similarly formed response from VDMS
and returns it to the client.
The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret the blobs field.
Currently, client libraries are implemented for Python and C++ client.
The client libraries are lightweight, as they simply implement the communication
protocol between the client and the server.
This makes it easier for developers to implement similar client libraries using
any other programming language of their choice.

>>>>

In this section, we further describe VDMS design principles and implementation,
which was briefly introduced in previous work \cite{vdms-nips}.

VDMS implements a client-server architecture that handles client
requests concurrently, and coordinates query execution across
the metadata and visual data components in order to return a unified response.
Users interact with both metadata and visual data
(i.e., images, videos, feature vectors) using a unified API,
in a transactional manner.
Figure \ref{fig:arch} depicts the high-level architecture of VDMS.

@@

The client library implements TCP/IP based connectors to the VDMS Server,
similar to most database\cite{memsql, mysql, postgresql}.
Users can connect to VDMS and implement queries using VDMS' API
by defining JSON commands conforming to the query protocol we have defined.
The client library provides a simple method that
accepts a JSON string and an array or vector of blobs.
Internally, the library wraps the query string and blobs using
Google Protobufs \cite{protobufs} and sends it to the VDMS server.
It also receives a similarly formed response from VDMS
and returns it to the client.
The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret the blobs field.
Currently, client libraries are implemented for Python and C++ client.
The client libraries are lightweight, as they simply implement the communication
protocol between the client and the server.
This makes it easier for developers to implement similar client libraries using
any other programming language of their choice.
